---
title: "Synopsis"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---


```{r set_options_global, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r define_paths}

path_reccap2 <-
  "/nfs/kryo/work/updata/reccap2/"

path_synoptic_datasets <-
  "/nfs/kryo/work/updata/reccap2/synoptic_datasets/"

```

```{r load_libraries_specific, include=FALSE}
library(tidyverse)
library(collapse)
library(patchwork)
library(stars)
library(lubridate)
library(gsw)
library(marelac)
library(colorspace)
```


```{r set_ggplot_theme_global, include = FALSE}
theme_set(theme_bw())
```

# Read data

region_name: 1.Atlantic, 2.Pacific, 3.Indian, 4.Arctic, 5.Southern  

atlantic  
    region_name: 1.NA SPSS, 2.NA STSS, 3.NA STPS, 4.AEQU, 5.SA STPS, 6.MED (not in FM14)
pacific  
    region_name: 1.NP SPSS, 2.NP STSS, 3.NP STPS, 4.PEQU-W, 5.PEQU-E, 6.SP STPS
indian  
    region_name: 1.Arabian Sea, 2.Bay of Bengal, 3.Equatorial Indian, 4.Southern Indian
arctic  
    region_name: 1.ARCTIC ICE (not in FM14), 2.NP ICE, 3.NA ICE, 4.Barents (not in FM14)
southern  
    region_name: 1.SO STSS, 2.SO SPSS, 3.SO ICE


```{r read files}

surface_co2 <-
  read_csv(
    file = paste(
      path_synoptic_datasets,
      "surface_co2_surface_biome_averages",
      ".csv",
      sep = ""
    )
  )

surface_co2 <- surface_co2 %>% 
  filter(model != "NIES-ML3_v20220222")

models <-
  read_csv(
    file = paste(
      path_synoptic_datasets,
      "models_surface_biome_averages",
      ".csv",
      sep = ""
    )
  )

biome_averages <- bind_rows(
  surface_co2 %>% mutate(class = "surface_co2"),
  models %>% mutate(class = "models")
)

biome_averages <- biome_averages  %>% 
  mutate(biome = case_when(
    biome == "atlantic_1" ~ "NA SPSS",
    biome == "atlantic_2" ~ "NA STSS",
    biome == "atlantic_3" ~ "NA STPS",
    biome == "atlantic_4" ~ "AEQU",
    biome == "atlantic_5" ~ "SA STPS",
    biome == "atlantic_6" ~ "MED",
    biome == "pacific_1" ~ "NP SPSS",
    biome == "pacific_2" ~ "NP STSS",
    biome == "pacific_3" ~ "NP STPS",
    biome == "pacific_4" ~ "PEQU-E",
    biome == "pacific_5" ~ "PEQU-W",
    biome == "pacific_6" ~ "SP STSS",
    biome == "indian_1" ~ "Arabian Sea",
    biome == "indian_2" ~ "Bay of Bengal",
    biome == "indian_3" ~ "Equatorial Indian",
    biome == "indian_4" ~ "Southern Indian",
    biome == "arctic_1" ~ "ARCTIC ICE",
    biome == "arctic_2" ~ "NP ICE",
    biome == "arctic_3" ~ "NA ICE",
    biome == "arctic_4" ~ "Barents",
    biome == "southern_1" ~ "SO STSS",
    biome == "southern_2" ~ "SO SPSS",
    biome == "southern_3" ~ "SO ICE",
    biome == "atlantic_2_pacific_2" ~ "STSS NA + NP",
    biome == "atlantic_3_pacific_3" ~ "STPS NA + NP",
    biome == "atlantic_5_pacific_6_indian_4" ~ "STPS SA + SP + SI",
    biome == "southern_1_southern_2" ~ "SO STSS + SPSS", 
    TRUE ~ "other"
  ))


```

# Filter biomes

```{r filter_biomes}

biome_averages <- biome_averages  %>%
  filter(biome %in% c("NA SPSS",
                      "NP SPSS",
                      "STSS NA + NP",
                      "STPS NA + NP",
                      "STPS SA + SP + SI",
                      "SO STSS + SPSS"))

biome_averages <- biome_averages %>% 
  mutate(date = paste(year,sprintf("%02d",month),"15", sep = "-"),
         date = as.Date(date, format = "%Y-%m-%d"))

```


# pCO2 - SST circles

```{r pCO2_sst_circles}

biome_average_class <- biome_averages %>%
  group_by(biome, month, class) %>%
  summarise(across(c("spco2", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class %>% 
  ggplot(aes(tos_mean, spco2_mean, col = class)) +
  geom_path() +
  geom_point() +
  facet_wrap(~biome)

biome_average_class_model <- biome_averages %>%
  group_by(biome, month, class, model) %>%
  summarise(across(c("spco2", "dissicos", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class_model %>% 
  ggplot(aes(tos_mean, spco2_mean, col = class, group = model)) +
  geom_path() +
  # geom_point() +
  facet_wrap(~biome)

biome_average_class_model %>% 
  ggplot(aes(tos_mean, dissicos_mean, col = class, group = model)) +
  geom_path() +
  # geom_point() +
  facet_wrap(~biome)

biome_average_class_year <- biome_averages %>%
  group_by(biome, date, class) %>%
  summarise(across(c("spco2", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class_year %>% 
  ggplot(aes(tos_mean, spco2_mean, col = date)) +
  geom_path() +
  scale_color_viridis_c() +
  # geom_point() +
  facet_grid(class~biome, scales = "free")


```




# Seasonal amplitude time series

```{r amplitude_time_series}

amplitudes <-
  biome_averages %>%
  select(year, month, biome, class, model, fgco2, fgco2_reg, spco2) %>% 
  pivot_longer(fgco2:spco2,
               names_to = "parameter",
               values_to = "value") %>% 
  group_by(class, model, year, biome, parameter) %>%
  summarise(min = min(value),
            max = max(value),
            amplitude = max - min) %>%
  ungroup()

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>% 
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col="black", se=FALSE) +
      labs(y = .x$parameter,
           title = "Seasonal amplitude (annual max - min)") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )


pdf("output/amplitude_time_series.pdf",
    width = 10,
    height = 10)
amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>% 
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col="black", se=FALSE) +
      labs(y = .x$parameter,
           title = "Seasonal amplitude (annual max - min)") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )
dev.off()

amplitudes %>%
  select(-amplitude) %>%
  pivot_longer(min:max,
               names_to = "extreme",
               values_to = "value") %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = extreme)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = .x$parameter,
           title = "Annual max & min") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )

pdf("output/min_max_time_series.pdf",
    width = 10,
    height = 10)
amplitudes %>%
  select(-amplitude) %>%
  pivot_longer(min:max,
               names_to = "extreme",
               values_to = "value") %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = extreme)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = .x$parameter,
           title = "Annual max & min") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )
dev.off()

```


