---
title: "Synopsis"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---


```{r set_options_global, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r define_paths}

path_reccap2 <-
  "/nfs/kryo/work/updata/reccap2/"

path_synoptic_datasets <-
  "/nfs/kryo/work/updata/reccap2/synoptic_datasets/"

```

```{r load_libraries_specific, include=FALSE}
library(tidyverse)
library(collapse)
library(patchwork)
library(stars)
library(lubridate)
library(gsw)
library(marelac)
library(colorspace)
```


```{r set_ggplot_theme_global, include = FALSE}
theme_set(theme_bw())

# definition colors for product classes

col_class <- c("#008C00", "#005AC8", "#A09600")


```


# Read data

region_name: 1.Atlantic, 2.Pacific, 3.Indian, 4.Arctic, 5.Southern  

atlantic  
    region_name: 1.NA SPSS, 2.NA STSS, 3.NA STPS, 4.AEQU, 5.SA STPS, 6.MED (not in FM14)
pacific  
    region_name: 1.NP SPSS, 2.NP STSS, 3.NP STPS, 4.PEQU-W, 5.PEQU-E, 6.SP STPS
indian  
    region_name: 1.Arabian Sea, 2.Bay of Bengal, 3.Equatorial Indian, 4.Southern Indian
arctic  
    region_name: 1.ARCTIC ICE (not in FM14), 2.NP ICE, 3.NA ICE, 4.Barents (not in FM14)
southern  
    region_name: 1.SO STSS, 2.SO SPSS, 3.SO ICE


```{r read files}

surface_co2 <-
  read_csv(
    file = paste(
      path_synoptic_datasets,
      "surface_co2_surface_biome_averages",
      ".csv",
      sep = ""
    )
  )

# surface_co2 <- surface_co2 %>% 
#   filter(model != "NIES-ML3_v20220222")

models <-
  read_csv(
    file = paste(
      path_synoptic_datasets,
      "models_surface_biome_averages",
      ".csv",
      sep = ""
    )
  )

biome_averages <- bind_rows(
  surface_co2 %>% mutate(class = "surface_co2"),
  models %>% mutate(class = "models")
)

biome_averages <- biome_averages  %>% 
  mutate(biome = case_when(
    biome == "atlantic_1" ~ "NA-SPSS",
    biome == "atlantic_2" ~ "NA-STSS",
    biome == "atlantic_3" ~ "NA-STPS",
    biome == "atlantic_4" ~ "AEQU",
    biome == "atlantic_5" ~ "SA-STPS",
    biome == "atlantic_6" ~ "MED",
    biome == "pacific_1" ~ "NP-SPSS",
    biome == "pacific_2" ~ "NP-STSS",
    biome == "pacific_3" ~ "NP-STPS",
    biome == "pacific_4" ~ "PEQU-E",
    biome == "pacific_5" ~ "PEQU-W",
    biome == "pacific_6" ~ "SP-STSS",
    biome == "indian_1" ~ "Arabian Sea",
    biome == "indian_2" ~ "Bay of Bengal",
    biome == "indian_3" ~ "Equatorial Indian",
    biome == "indian_4" ~ "Southern Indian",
    biome == "arctic_1" ~ "ARCTIC-ICE",
    biome == "arctic_2" ~ "NP-ICE",
    biome == "arctic_3" ~ "NA-ICE",
    biome == "arctic_4" ~ "Barents",
    biome == "southern_1" ~ "SO-STSS",
    biome == "southern_2" ~ "SO-SPSS",
    biome == "southern_3" ~ "SO-ICE",
    biome == "atlantic_2_pacific_2" ~ "NH-STSS",
    biome == "atlantic_3_pacific_3" ~ "NH-STPS",
    biome == "atlantic_5_pacific_6_indian_4" ~ "SH-STPS",
    biome == "southern_1_southern_2" ~ "SH-SS", 
    TRUE ~ "other"
  ))


```

# Filter biomes

```{r filter_biomes}

biome_averages <- biome_averages  %>%
  filter(biome %in% c("NA-SPSS",
                      "NP-SPSS",
                      "NH-STSS",
                      "NH-STPS",
                      "SH-STPS",
                      "SH-SS"))

biome_averages <- biome_averages %>% 
  mutate(date = paste(year,sprintf("%02d",month),"15", sep = "-"),
         date = as.Date(date, format = "%Y-%m-%d"))

```


# pCO2 - SST circles

```{r pCO2_sst_circles}

biome_average_class <- biome_averages %>%
  group_by(biome, month, class) %>%
  summarise(across(c("spco2", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class %>% 
  ggplot(aes(tos_mean, spco2_mean, col = class)) +
  geom_path() +
  geom_point() +
  facet_wrap(~biome)

biome_average_class_model <- biome_averages %>%
  group_by(biome, month, class, model) %>%
  summarise(across(c("spco2", "dissicos", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class_model %>% 
  ggplot(aes(tos_mean, spco2_mean, col = class, group = model)) +
  geom_path() +
  # geom_point() +
  facet_wrap(~biome)

biome_average_class_model %>% 
  ggplot(aes(tos_mean, dissicos_mean, col = class, group = model)) +
  geom_path() +
  # geom_point() +
  facet_wrap(~biome)

biome_average_class_year <- biome_averages %>%
  group_by(biome, date, class) %>%
  summarise(across(c("spco2", "tos"), list(mean = mean, sd = sd), na.rm = TRUE)) %>%
  ungroup()

biome_average_class_year %>% 
  ggplot(aes(tos_mean, spco2_mean, col = date)) +
  geom_path() +
  scale_color_viridis_c() +
  # geom_point() +
  facet_grid(class~biome, scales = "free")


```




# Seasonal amplitude time series

```{r formatting}

biome_averages <- biome_averages %>% 
  mutate(class = case_when(class == "models" ~ "GOBMs",
                           class == "surface_co2" ~ "pCO2 products",
                           TRUE ~ class))

flux_amp_title <- expression("Integrated flux amplitude" ~ (Pg ~ C ~ yr ^ {-1}))
flux_int_title <- expression("Integrated flux" ~ (Pg ~ C ~ yr ^ {-1}))

pCO2_amp_title <- expression(pCO[2] ~ amplitude ~ (µatm))
pCO2_title <- expression(pCO[2] ~ (µatm))

```

```{r seasonal_cycles_per_biome}

biome_averages %>% 
  ggplot(aes(month, fgco2_reg, col=year, group = interaction(year, model))) +
  geom_path() +
  scale_color_viridis_c() +
  facet_grid(biome ~ class) +
  scale_x_continuous(breaks = seq(1,12,3))

# library(khroma)

biome_averages %>% 
  filter(class == "GOBMs") %>% 
  ggplot(aes(month, fgco2_reg, col=model, group = interaction(year, model))) +
  geom_hline(yintercept = 0) +
  geom_path() +
  scale_color_brewer(palette = "Paired") +
  facet_grid(biome ~ class) +
  labs(y = flux_int_title) +
  scale_x_continuous(breaks = seq(1,12,3))

biome_averages %>% 
  filter(class != "GOBMs") %>% 
  ggplot(aes(month, fgco2_reg, col=model, group = interaction(year, model))) +
  geom_hline(yintercept = 0) +
  geom_path() +
  scale_color_brewer(palette = "Paired") +
  facet_grid(biome ~ class) +
  labs(y = flux_int_title) +
  scale_x_continuous(breaks = seq(1,12,3))

```




```{r min_max_individual_products}

amplitudes <-
  biome_averages %>%
  select(year, month, biome, class, model, fgco2, fgco2_reg, spco2) %>% 
  pivot_longer(fgco2:spco2,
               names_to = "parameter",
               values_to = "value") %>% 
  group_by(class, model, year, biome, parameter) %>%
  summarise(min = min(value),
            max = max(value),
            amplitude = max - min) %>%
  ungroup()

amplitudes_all_parameter <- amplitudes

amplitudes <- amplitudes %>% 
  filter(parameter == "fgco2_reg")

amplitudes %>%
  group_split(class) %>%
  head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = .x$parameter,
           title = "Seasonal amplitude (annual max - min)") +
      scale_color_brewer(palette = "Paired", name = "product") +
      facet_grid(biome ~ ., scales = "free_y")
  )


pdf("output/amplitude_min_max_individual_products.pdf",
    width = 8,
    height = 4)

amplitudes %>%
  group_split(class, biome) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      # geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = flux_amp_title,
           title = .x$biome) +
      scale_color_brewer(palette = "Paired", name = .x$class) +
      theme(axis.title.x = element_blank())
  )

dev.off()

amplitudes %>%
  select(-amplitude) %>%
  pivot_longer(min:max,
               names_to = "extreme",
               values_to = "value") %>%
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = extreme)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = .x$parameter,
           title = "Annual max & min") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )

pdf("output/min_max_individual_products.pdf",
    width = 12,
    height = 6)

amplitudes %>%
  select(-amplitude) %>%
  pivot_longer(min:max,
               names_to = "extreme",
               values_to = "value") %>%
  group_split(class, biome) %>%
  head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = extreme)) +
      geom_path(aes(col = model)) +
      # geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = flux_int_title,
           title = .x$biome) +
      scale_color_brewer(palette = "Paired", name = .x$class) +
      theme(axis.title.x = element_blank())
  )

dev.off()

```


```{r min_max_ensemble_all_GOBM}

amplitudes <-
  amplitudes %>% 
  group_by(class, year, biome, parameter) %>%
  summarise(min_mean = mean(min),
            min_sd = sd(min),
            max_mean = mean(max),
            max_sd = sd(max),
            amplitude_mean = mean(amplitude),
            amplitude_sd = sd(amplitude)) %>%
  ungroup() 
  

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ ., scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )


pdf("output/amplitude_min_max_ensemble.pdf",
    width = 8,
    height = 6)

amplitudes %>%
  filter(parameter == "fgco2_reg") %>%
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = flux_amp_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      coord_cartesian(expand = 0) +
      facet_wrap(biome ~ .
                 , scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, min_mean,
                    col = class,
                    linetype = "Annual mininmum")) +
      geom_path(aes(year, max_mean,
                    col = class,
                    linetype = "Annual maximum")) +
      geom_ribbon(aes(year, min_mean,
                      ymin = min_mean - min_sd,
                      ymax = min_mean + min_sd,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, max_mean,
                      ymin = max_mean - max_sd,
                      ymax = max_mean + max_sd,
                      fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

pdf("output/min_max_ensemble_all_GOBMs.pdf",
    width = 6,
    height = 4)

amplitudes %>%
  group_split(biome) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, min_mean,
                    col = class,
                    linetype = "Annual mininmum")) +
      geom_path(aes(year, max_mean,
                    col = class,
                    linetype = "Annual maximum")) +
      geom_ribbon(aes(year, min_mean,
                      ymin = min_mean - min_sd,
                      ymax = min_mean + min_sd,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, max_mean,
                      ymin = max_mean - max_sd,
                      ymax = max_mean + max_sd,
                      fill = class), alpha = 0.2) +
      labs(y = flux_int_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()

```


```{r min_max_ensemble_excl_MPIOM-HAMOCC}

amplitudes <-
  amplitudes_all_parameter %>% 
  filter(model != "MPIOM-HAMOCC_v20220110") %>% 
  group_by(class, year, biome, parameter) %>%
  summarise(min_mean = mean(min),
            min_sd = sd(min),
            max_mean = mean(max),
            max_sd = sd(max),
            amplitude_mean = mean(amplitude),
            amplitude_sd = sd(amplitude)) %>%
  ungroup() 

amplitudes_all_parameter <- amplitudes

amplitudes <- amplitudes %>% 
  filter(parameter == "fgco2_reg")
  

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ ., scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )


pdf("output/amplitude_min_max_ensemble.pdf",
    width = 8,
    height = 6)

amplitudes %>%
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = flux_amp_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      coord_cartesian(expand = 0) +
      scale_y_continuous(breaks = seq(-10,10,0.25)) +
      facet_wrap(biome ~ .
                 , scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank(),
            panel.grid = element_blank())
  )

dev.off()

pdf("output/amplitude_min_max_ensemble_pCO2.pdf",
    width = 8,
    height = 6)

amplitudes_all_parameter %>%
  filter(parameter == "spco2") %>% 
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = pCO2_amp_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      coord_cartesian(expand = 0) +
      scale_y_continuous(breaks = seq(0,100,10)) +
      facet_wrap(biome ~ .
                 , scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank(),
            panel.grid = element_blank())
  )

dev.off()

pdf("output/min_max_ensemble_pCO2.pdf",
    width = 8,
    height = 6)


amplitudes_all_parameter %>%
  filter(parameter == "spco2") %>%
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(data = .x) +
      geom_path(aes(
        year, min_mean,
        col = class,
        linetype = "Annual mininmum"
      )) +
      geom_path(aes(
        year, max_mean,
        col = class,
        linetype = "Annual maximum"
      )) +
      geom_ribbon(
        aes(
          year,
          min_mean,
          ymin = min_mean - min_sd,
          ymax = min_mean + min_sd,
          fill = class
        ),
        alpha = 0.2
      ) +
      geom_ribbon(
        aes(
          year,
          max_mean,
          ymin = max_mean - max_sd,
          ymax = max_mean + max_sd,
          fill = class
        ),
        alpha = 0.2
      ) +
      labs(y = pCO2_title) +
      scale_y_continuous(breaks = seq(0,1000,20)) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y") +
      coord_cartesian(expand = 0) +
      theme(
        legend.title = element_blank(),
        axis.title.x = element_blank(),
        panel.grid = element_blank()
      )
  )

dev.off()

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, min_mean,
                    col = class,
                    linetype = "Annual mininmum")) +
      geom_path(aes(year, max_mean,
                    col = class,
                    linetype = "Annual maximum")) +
      geom_ribbon(aes(year, min_mean,
                      ymin = min_mean - min_sd,
                      ymax = min_mean + min_sd,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, max_mean,
                      ymin = max_mean - max_sd,
                      ymax = max_mean + max_sd,
                      fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

pdf("output/min_max_ensemble_excl_MPIOM-HAMOCC.pdf",
    width = 6,
    height = 4)

amplitudes %>%
  group_split(biome) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, min_mean,
                    col = class,
                    linetype = "Annual mininmum")) +
      geom_path(aes(year, max_mean,
                    col = class,
                    linetype = "Annual maximum")) +
      geom_ribbon(aes(year, min_mean,
                      ymin = min_mean - min_sd,
                      ymax = min_mean + min_sd,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, max_mean,
                      ymin = max_mean - max_sd,
                      ymax = max_mean + max_sd,
                      fill = class), alpha = 0.2) +
      labs(y = flux_int_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      scale_y_continuous(breaks = seq(-10,10,0.5)) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank(),
            panel.grid = element_blank(),
            strip.background = element_blank())
  )

dev.off()

```


```{r seasons_individual}


seasons <-
  biome_averages %>%
  mutate(season = seas::mkseas(date, width = "JFM")) %>%
  filter(season %in% c("JFM", "JAS")) %>% 
  select(season, year, biome, class, model, fgco2, fgco2_reg, spco2) %>% 
  pivot_longer(fgco2:spco2,
               names_to = "parameter",
               values_to = "value") %>% 
  group_by(class, model, year, season, biome, parameter) %>%
  summarise(value = mean(value)) %>%
  ungroup()


seasons %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = season)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = .x$parameter,
           title = "Annual max & min") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )

pdf("output/seasonal_individual_products.pdf",
    width = 10,
    height = 10)

seasons %>%
  filter(parameter == "fgco2_reg") %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, value, linetype = season)) +
      geom_path(aes(col = model)) +
      # geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = flux_int_title) +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()



amplitudes <-
  seasons %>% 
  pivot_wider(names_from = season,
              values_from = value) %>% 
  mutate(amplitude = JAS - JFM)
  


amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      geom_smooth(method = "lm", col="black", se=FALSE) +
      labs(y = .x$parameter,
           title = "Seasonal amplitude (annual max - min)") +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y")
  )


pdf("output/amplitude_seasonal_individual_products.pdf",
    width = 10,
    height = 10)

amplitudes %>%
  filter(parameter == "fgco2_reg") %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(data = .x,
             aes(year, amplitude)) +
      geom_path(aes(col = model)) +
      # geom_smooth(method = "lm", col = "black", se = FALSE) +
      labs(y = flux_amp_title) +
      scale_color_discrete(name = "product") +
      facet_grid(biome ~ class, scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()


```


```{r seasons_ensemble}


seasons <-
  seasons %>%
  group_by(class, year, season, biome, parameter) %>%
  summarise(mean = mean(value),
            sd = sd(value)) %>%
  ungroup() %>% 
  filter(season %in% c("JFM", "JAS")) %>% 
  pivot_wider(names_from = season,
              values_from = c(mean, sd))


seasons %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, mean_JFM,
                    col = class,
                    linetype = "JFM")) +
      geom_path(aes(year, mean_JAS,
                    col = class,
                    linetype = "JAS")) +
      geom_ribbon(aes(year, mean_JFM,
                      ymin = mean_JFM - sd_JFM,
                      ymax = mean_JFM + sd_JFM,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, mean_JAS,
                      ymin = mean_JAS - sd_JAS,
                      ymax = mean_JAS + sd_JAS,
                      fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

pdf("output/seasonal_ensemble.pdf",
    width = 8,
    height = 6)

seasons %>%
  filter(parameter == "fgco2_reg") %>% 
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x
    ) +
      geom_hline(yintercept = 0) +
      geom_path(aes(year, mean_JFM,
                    col = class,
                    linetype = "JFM")) +
      geom_path(aes(year, mean_JAS,
                    col = class,
                    linetype = "JAS")) +
      geom_ribbon(aes(year, mean_JFM,
                      ymin = mean_JFM - sd_JFM,
                      ymax = mean_JFM + sd_JFM,
                      fill = class), alpha = 0.2) +
      geom_ribbon(aes(year, mean_JAS,
                      ymin = mean_JAS - sd_JAS,
                      ymax = mean_JAS + sd_JAS,
                      fill = class), alpha = 0.2) +
      labs(y = flux_int_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ .
                 , scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()


amplitudes <-
  amplitudes %>%
  group_by(class, year, biome, parameter) %>%
  summarise(amplitude_mean = mean(amplitude),
            amplitude_sd = sd(amplitude)) %>%
  ungroup()
  

amplitudes %>%
  group_split(parameter) %>%
  # head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = .x$parameter) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      facet_wrap(biome ~ ., scales = "free_y"
      ) +
      coord_cartesian(expand = 0) +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )


pdf("output/amplitude_seasonal_ensemble.pdf",
    width = 8,
    height = 6)

amplitudes %>%
  filter(parameter == "fgco2_reg") %>%
  group_split(parameter) %>%
  head(1) %>%
  map(
    ~ ggplot(
      data = .x,
      aes(
        year,
        amplitude_mean,
        ymin = amplitude_mean - amplitude_sd,
        ymax = amplitude_mean + amplitude_sd
      )
    ) +
      geom_path(aes(col = class)) +
      geom_ribbon(aes(fill = class), alpha = 0.2) +
      labs(y = flux_amp_title) +
      scale_color_manual(values = col_class, name = "product") +
      scale_fill_manual(values = col_class, name = "product") +
      coord_cartesian(expand = 0) +
      facet_wrap(biome ~ .
                 , scales = "free_y") +
      theme(legend.title = element_blank(),
            axis.title.x = element_blank())
  )

dev.off()

```


